\tolerance=10001

\documentclass[12pt]{report}

% useful packages
\usepackage{graphicx}
\usepackage{float}
\usepackage{multirow}
\usepackage{longtable}


%Use this package and option to label equations, e.g. chapter 1 equation 2 is labeled as (1.2)

\usepackage{amsmath}
\numberwithin{equation}{chapter}

%Use this package to label figures and tables similarly to equations above

\usepackage[figurewithin=chapter]{caption}
\usepackage[tablewithin=chapter]{caption}

% Use this package to include URLs
\usepackage{url}
%\usepackage{hyperref}

% Supresses citations in TOC so that numbering is correct in document
\usepackage{notoccite}

%%%%%Other LaTeX2e packages such as the AMS fonts and graphics packages can be included here.

%This package is built on the LaTeX2e report class, so any other packages which are
%also compatible with it can also be used in combination with it.  ODUthesis should
%be in the directory in which you are working, or in one of the standard input directories
%for the TeX installation on your system.

\usepackage{ODUthesis}

%This package causes the first line of a section to be indented as required by the dissertation guide.

\usepackage{indentfirst}

%This style follows conventions used in Physical Review C. The names of figures, tables and captions can
%be changed by using the commands below with appropriate changes. For example, "FIG." could be replaced by
%"Fig." or "Figure" to change the labeling of figure captions.

%\renewcommand{\figurename}{FIG.}
%\renewcommand{\tablename}{TABLE}
%\renewcommand{\bibname}{BIBLIOGRAPHY}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% My Custom Commands %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\thetaC}{\theta_{C}} % shortcut for cherenkov angle
\newcommand{\diff}{\mathrm{d}} % differential d for math
\newcommand{\unit}[1]{\text{ #1}}
%\newcommand{\quote}[1]{``#1''}

% Define paths to figures and plots
\graphicspath{{./figures/}{./plots/}{./plots/thetaC/}}

%% Set of commands to allow commenting in bold red
%% and listing all comments with page number
%% before introductory chapter
%\usepackage{tocloft}
%\newcommand{\listcomments}{Comments}
%\newlistof{comments}{comm}{\listcomments}
%\newcommand{\comment}[1]{%
%	\refstepcounter{comments}%
%	\textbf{\large \pdfliteral{1 0 0 rg} #1 \pdfliteral{0 0 0 rg}}%
%	\addcontentsline{comm}{comments}{{\large \pdfliteral{1 0 0 rg} #1 \pdfliteral{0 0 0 rg}}}
%} % add big colored comment to text so it's easily identified later

\begin{document}

\title{R\&D of a High-Performance DIRC Detector for a future Electron-Ion Collider}

\author{Stacey Lee Allison}
\principaladviser{Charles Hyde}
%\member{Gagik Gavalian}
\member{Mark Havey}
\member{Grzegorz Kalicy}  %This command produces a signature line for the specified member on the
\member{Jay Van Orden}
\member{Mike Overstreet}  %title page. Use on instance of this command for each member of the
                   %committee other than the advisor up to a total of 5 members.

\degrees{B.S. May 2012, University of North Georgia \\
B.S. May 2012, University of North Georgia \\
M.S. May 2014, Old Dominion University}
\dept{Physics}          %for example \dept{physics}

\submitdate{August 2017}

%\phdfalse          %produces language on title page for Masters Thesis. 
                    %otherwise the default is for a Ph.D. dissertation.

%\copyrightfalse    %suppresses copyright notice

%\figurespagefalse  %suppresses List of Figures

%\tablespagefalse   %suppresses List of Tables

\vita{
\textbf{}\\
\textbf{Education}\\ 
\\
Old Dominion University, Norfolk, VA\\
\begin{itemize}
\item PhD Candidate in experimental nuclear physics, 2012--Present\\
\item Master of Science, 2014\\
\end{itemize}
University of North Georgia, Dahlonega, GA\
\begin{itemize}
\item Bachelor of Science in Physics, 2012\\
\item Bachelor of Science in Mathematics, 2012\\
\item Minor in Computer Science, 2012
\end{itemize}
\textbf{Research Experience}\\
\begin{itemize}
\item 2015--Present: Graduate research assistant studying and optimizing the design of Electron-Ion Collider DIRC detector via hardware component tests and extensive Monte Carlo simulation.\\
\item 2013--2015: Graduate research assistant running simulations and building electromagnetic calorimeter crystals for the Jefferson Lab Hall A DVCS experiment at Old Dominion University clean room.\\
\end{itemize}
\textbf{Publications}\\
\begin{itemize}
\item L. Allison, et al., ``High-performance DIRC detector for use in an Electron-Ion Collider", PoS, \textbf{ICHEP} (2016) 300.\\
\item V. Sulkosky, et al., ``Studies of relative gain and timing response of fine-mesh photomultiplier tubes in high
magnetic fields", NIST A, \textbf{827} (2016) 137.\\
\item G. Kalicy, et al., ``High-performance DIRC detector for the future Electron Ion Collider experiment", JINST, \textbf{11} (2016) C07015. \\
\item Y. Ilieva, et al., ``MCP-PMT studies at the High-B test facility at Jefferson Lab", JINST, \textbf{11} (2016) C03061.
\end{itemize}
}


\abstract{An Electron-Ion Collider (EIC) is proposed as the next big scientific facility to be built in the United States, costing over \$1 billion in design and construction. 
Each detector concept for the electron/ion beam interaction point is integrated into a large solenoidal magnet. 
The necessity for excellent hadronic particle identification (pion/kaon/proton) in the barrel region of the solenoid has pushed research and development (R\&D) towards a new, high-performance Detection of Internally Reflected Cherenkov light (DIRC) detector design. 
The passage of a high energy charged particle through a fused silica bar of the DIRC generates optical Cherenkov radiation. 
A large fraction of this light propagates by total internal reflection to the end of the bar, where the photon trajectories expand in a large volume before reaching a highly segmented photo-detector array. 
The spatial and temporal distribution of the Cherenkov light at the photo-detector array allows one to reconstruct the angle of emission of the light relative to the incident charged particle track.
In order to reach the desired performance of $3\sigma$ $\pi/K$ separation at 6 GeV/c particle momentum a new 3-layer spherical lens focusing optic with a lanthanum crown glass central layer was designed to have a nearly flat focal plane. 
In order to validate the EIC DIRC simulation package, a synergistic test beam campaign was carried out in 2015 at the CERN PS with the PANDA Barrel DIRC group using a prototype DIRC detector. 
Along with the analysis of the CERN test beam data, measurements of the focal plane of the 3-layer lens were performed using a custom-built laser setup at Old Dominion University. 
Radiation hardness of the lanthanum crown glass was tested using a 160~keV X-ray source and a monochromator at the Catholic University of America. Results of these test-bench experiments and the analysis of the 2015 CERN test beam data are presented here.}

\beforepreface

\prefacesection{Acknowledgements}
    %text of Acknowledgements goes here, any other preface section is inserted similarly by the command \prefacesection{Section Title}
The work presented in this manuscript was carried out with support from the U.S. Department of Energy, the Brookhaven National Laboratory "Generic Detector R\&D Program for the EIC" (eRD14), and GSI Helmholtzzentrum f\"ur Schwerionenforschung GmbH.
\\~\\
I would like to thank my thesis advisor, Dr. Charles Hyde, for his patience  and understanding in allowing me to work on a project that I truly enjoy.
\\~\\
I would like to thank my thesis supervisor, Dr. Grzegorz Kalicy, for all of his guidance in learning DIRC technology. 
\\~\\
I would like to thank my collaborators at GSI for giving me the opportunity to experience working hands-on with a DIRC detector.
\\~\\
Finally, I would like to thank all my friends and family, especially my parents Jennifer and Stacy Allison. Without their love and support I would not be where I am today.

\afterpreface

%\listofcomments

    %The text of the thesis/dissertation begins here. The basic organization is in chapters, sections, subsections. 

\chapter{Introduction}
\input{chapters/introduction} % intro, eic, etc

\chapter{Electron-Ion Collider}
\input{chapters/eic} % description of EIC and why it's needed

\chapter{DIRC Technology}
\input{chapters/dirc} % explination of DIRC technology

\chapter{High-Performance DIRC@EIC}
\input{chapters/eicdirc} % specifications of high-performance DIRC@EIC

\chapter{Testing DIRC Components}
\input{chapters/components} % testing lens focal plane and rad hardness, and MCP-PMTs

\chapter{3-Layer Lens Performance in A Particle Beam}
\input{chapters/analysis} % analysis results from CERN 2015 test beam

\chapter{Summary and Outlook}
\input{chapters/summary} % outlook of future work and summary of results

  %This begins the list of reference or bibliography.
  %The default form is consistent with the references in the Physical Review.
  %The articles must be listed in the order in which they appear in the text.
  %The style of the bibliography can be changed and automatic ordering of the entries can be accomplished using BibTeX.
  %Use of BibTeX is explained in most of the standard LaTeX books.

\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}  %This command adds and entry for the bibliography in the table of contents

\bibliography{bibliography}{}
\bibliographystyle{unsrt}

%A new command for appendix chapters has been defined called \achapter that has been modified
%so that it can add the appendices to the table of contents in the approved form.

\appendix

\setlength\LTcapwidth{\textwidth}
\achapter{Geometric Reconstruction Fitting Parameters}
\input{chapters/app_fitting}

\achapter{Error Evaluation for Geometric Reconstruction}
\input{chapters/app_error}

\newpage

%The command below initiates printing of the vita page. The name and other information is taken from previous entries.

\vitapage

\end{document}
